---
title: "Part_4_CreateHistogram"
output: html_document
---
I think the the next thing to try is to make these iterable. So, I'd like you to produce a histogram of origin times found in simulations

**You could do that either by doing a simulation from a bunch of rows from the posterior trace or by simulating a bunch of trees from one row of the trace.**

Either way, do about a hundred simulations and make a histogram of them. Add a vertical line to the histogram at 131 million years - the empirical value uncovered in Christina's work. This will give us a visual check on the simulations
-get the origin for every hundred simulations
-do that for the number of fossils too

See the Part_4_CreateHistogramsSPEC. Rmd file on github or on the spec for the work

Other stuff I tried, but didn't work
```{r}
#lapply(x = vector/list of values that input to the function, FUN = function applied to each element of x/resultFBD)
```
could use x = list of values from the resultFBD, function is modifiedsfrt 
resultFBD <- modifiedSFBD(666, 1, mynewfoss, lambda = "lambda", mu = "mu", psi = c("psi.1.", "psi.2."), 1426, c(0, 61))


Maybe I want to run the simulations a bunch of times first. Store those results in a dataframe.
```{r}
n <- 3
lapply_result <- lapply(rep(1,n), resultFBD) #This won't work bc x is the input to the func
```
by creating a function that runs the simulation a bunch of times first
store that in a data frame
then apply the summary stat func to the data set...

Just simulate trees a bunch of times first
```{r}
for(i in 1:3){
  resultFBD <- modifiedSFBD(666, 1, mynewfoss, lambda = "lambda", mu = "mu", psi = c("psi.1.", "psi.2."), 1426, c(0, 61))
  
}

multiple_sim <- function(x) {
 #struggles
}

trial <- replicate(2, modifiedSFBD(666, 1, mynewfoss, lambda = "lambda", mu = "mu", psi = c("psi.1.", "psi.2."), 1426, c(0, 61)))
```
#replicate ended up creating a list of 4 objects. Soooo not good, for when you apply tree max and need to do [[2]][[1]]
