---
title: "Part_3_SummaryStatistics"
output: html_document
---
https://www.rdocumentation.org/packages/FossilSim/versions/2.1.1


```{r}
getwd()
mynewfoss <- read.table("C:\\Users\\shrey\\Desktop\\WrightLab\\shreya_foss_3.log", head = TRUE)
library(FossilSim)
```

for each i that is in the sequence psi, you execute the code chunk: append/add to p1 the column i from the data frame
```{r}
SFBD <- function(n_extant, n_trees, df, lambda, mu, psi, row, mers){
  lmu <- length(c(mu))
  lla <- length(c(lambda))
  lps <- length(c(psi))
  num <- max(c(lmu, lla, lps))
  
  if(length(mu) == 1){
    m1 <- rep(df[row, mu], times = num)} else{ 
      m1 <- c()
      for(i in mu){m1 <- append(m1, df[row, i])}}
  
  if(length(lambda) == 1){
    l1 <- rep(df[row, lambda], times = num)} else{
      l1 <- c()
      for(i in lambda){l1 <- append(l1, df[row, i])}}
  
  if(length(psi) == 1){
    p1 <- rep(df[row, psi], times = num)} else{
      p1 <- c()
      for(i in psi){p1 <- append(p1, df[row, i])}} #add to p1
  
  modelledfoss <- sim.fbd.rateshift.taxa(n_extant, n_trees, l1, m1, p1, times = mers, complete = TRUE)
  return(modelledfoss)
}

result <- SFBD(666, 1, mynewfoss, lambda = "lambda", mu = "mu", psi = c("psi.1.", "psi.2."), 244, c(0, 61))
```
Output for phylo object looks like: 

Phylogenetic tree with 677 tips and 676 internal nodes.

Tip labels:
	t477_1, t553_1, t51_1, t69_1, t255_1, t186_1, ...

Rooted; includes branch lengths.
----------------------------------------------------------------

**sim.fbd.rateshift.taxa simulates fossilized birth death trees (FBD) w/ incorporated rate shifts
*output is SAtrees with n extant sampled tips - got a LIST of phylo objects. Therefore, 'result' is an object of the class phylo

Find some info about structure of 'result'
http://www.phytools.org/eqg/Exercise_3.2/ to help understand what a phylo object is
```{r}
str(result)
class(result) #is a "list"
```


Functions this week: (1)count.fossils; (2)count.fossils.binned; (3)tree.max
(1) and (2) takes on fossils object. 

So, create a fossil record object
```{r}
fossils (data = result, from.taxonomy = FALSE)
as.fossils(result, from.taxonomy = FALSE)
is.fossils(result)
```

(1) count.fossils : count the total number of fossils
    	-count.fossils(fossils object)
      -output: number of extinct samples

- count.fossils.binned : count the total number of fossils per interval
	Count.fossils.binned(fossils, interval.ages)
		Interval.ages: vector of interval ages, starting with the min age of the youngest interval and ending w the maximum age of the oldest interval
		Output: vector of extinct samples corresponding to each interval. Note the last value corresponds to the number of samples > max age of the oldest interval.

- tree.max : find the maximum age in a phylo object (root age/origin time)
	Tree.max(t_the_phylo_object, root.edge = FLASE). 
		If true, include the root edge
	Output: max age


```{r}
count.fossils(result) #output 0
count.fossils.binned(result, c(0,61)) #output 0,0
tree.max(result, root.edge = 4.347512)
```

