---
title: "Part_5_Fossils_Visualize"
output: html_document
---
```{r}
mynewfoss <- read.table("C:\\Users\\shrey\\Desktop\\WrightLab\\shreya_foss.log", head = TRUE)
```

names(mynewfoss): shows that yes, there are fossil columns. "fossil.1." goes on till 29.
because theres 29 taxa. Also have corresponding t.1. to t.29.
```{r}
View(names(mynewfoss)) #find fossil.1. and other names
View(mynewfoss$fossil.1.)

```
- all negative values in fossils.#

Looked at the model_FBDP_TEFBD.Rev directory on gitbash: try to understand what these variables mean
foss_int.tsv file is read to 'intervals', includes a taxon name, a min and max
    fossil[i] is a uniform distribution of t[i]-min and t[i] - max
    t[i] is: tmrca(fbd_tree, clade(taxon)). tmrca is to find the most recent common ancestor. arguments are the tree and clade value.
    
All this (fossil and t) were in one for loop, going from 1:intervals.size(). intervals reads the .tsv file, and the size/length of it is 29. hence, got 29 fossil.#. and t.#.


