
---
title: "Part_3_SummaryStatistics"
output: html_document
---
https://www.rdocumentation.org/packages/FossilSim/versions/2.1.1
[Paper about FossilSim]https://doi.org/10.1111/2041-210X.13170


```{r}
mynewfoss <- read.table("C:\\Users\\shrey\\Desktop\\WrightLab\\shreya_foss_3.log", head = TRUE)
library(FossilSim)
```


**sim.fbd.rateshift.taxa** output is SAtrees with n extant sampled tips - got a LIST of phylo objects. Therefore, 'result' is an object of the class phylo
http://www.phytools.org/eqg/Exercise_3.2/ to help understand what a phylo object is
```{r}
str(result) #structure of result - what's in it
class(result) #is a "list"
str(result[[1]]$edge) #num [1:1366, 1:2] 685 686 950...
#More about the rateshift function, can be viewed as follows: function w/o the brackets
sim.fbd.rateshift.taxa
View(sim.fbd.rateshift.taxa) 
```

Functions this week: (1)count.fossils; (2)count.fossils.binned; (3)tree.max

(1) and (2) takes on fossils object. 

IGNORE IGNORE: 
----------------------------------------------------------------
tried: create a fossil record object
```{r}
fossils (data = result[[1]], from.taxonomy = FALSE)
as.fossils(data = df, from.taxonomy = FALSE)
is.fossils(result)
```
Error, cannot coerce class 'c("SAtree",..) to a data.frame

So, this chunk is a bunch of bleh. 
```{r}
fossils_func <- function(data) {
  return(fossils(result, from.taxonomy = F))
}
df <- data.frame(c('fossils_func'), stringsAsFactors = F)
do.call('[' result, 685)['edge'] # as if extracting: result[[1]]$edge
#want to put it in a dataframe MAYBE
as.data.frame(result) #same error: cannot coerce class to a data.frame
is.data.frame(result) #false
my_df <- lapply(result, "[", c('edge', 'tip.label', 'edge.length'))
is.data.frame(my_df) #false
edge = result[[1]][["edge"]]
sp = result[[1]][["tip.label"]]
hmin = min(result[[1]][["edge.length"]])
hmax
#no idea where I was going w this
library(plyr)
df_two <- ldply(result[[1]], data.frame) #a messy df:col names switched w rows
#data.frame(..., row.names = [result[[1]], ])
```
-----------------------------------------------------------------
IGNORE ABOVE 

#Not working yet
(1) count.fossils : Counts the total number of fossils
    	- count.fossils(fossils object). Input is dataframe or list
      - output: Number of extinct samples
(2) count.fossils.binned : Count the total number of fossils per interval
	    - Count.fossils.binned(fossils, interval.ages)
		  - Interval.ages: vector of interval ages, starting with the min age of the youngest interval and         ending w the maximum age of the oldest interval
		  - Output: vector of extinct samples corresponding to each interval. Note the last value corresponds to the number of samples > max age of the oldest interval.
```{r}
count.fossils(result[[1]]) #output 0
count.fossils.binned(result[[1]], c(0,61)) #output 0,0
```

#Worked: tree.max
(3) tree.max : find the maximum age in a phylo object (root age/origin time)
	- Tree.max(t_the_phylo_object, root.edge = F/T). 
		    - If true, includes the root edge (which we have in result)
	- Output: max age/origin time/root edge (when TRUE)
	
```{r}
origin_time <- tree.max(result[[1]], root.edge = TRUE) #output numeric: 91.89
```

printing the fossils object directly from the sim.fbd.rateshift.taxa() function


Was getting trouble with n.ages (could not find func.). So as C said, went on FossilSim's github to find it: https://github.com/fossilsim/fossilsim/blob/master/R/utils.R
```{r}
n.ages <- function(tree){
  depth = ape::node.depth.edgelength(tree)
  node.ages = max(depth) - depth
  names(node.ages) <- 1:(tree$Nnode+length(tree$tip))
  # adding possible offset if tree fully extinct
  if(!is.null(tree$root.time)) node.ages = node.ages + tree$root.time - max(node.ages)
  return(node.ages)
}
```

modify sim.fbd.rateshift.taxa to return a list of both fossils object(f) and the tree. Named sfrt
```{r}
sfrt <- function (n, numbsim, lambda, mu, psi, times, complete = FALSE) 
{
  if (length(lambda) != length(times)) 
    stop("Length mismatch between rate shift times and birth rates")
  if (length(mu) != length(times)) 
    stop("Length mismatch between rate shift times and death rates")
  if (length(psi) != length(times)) 
    stop("Length mismatch between rate shift times and sampling rates")
  
  trees = TreeSim::sim.rateshift.taxa(n, numbsim, lambda, 
    mu, rep(1, length(times)), times, complete = TRUE)
  
  for (i in 1:length(trees)) {
    t = trees[[i]]
    origin = max(n.ages(t)) + t$root.edge
    horizons = c(times, origin)
    f <- sim.fossils.intervals(tree = t, interval.ages = horizons, 
      rates = psi)
    tree = SAtree.from.fossils(t, f)
    node.ages = n.ages(tree)
    
    if (complete == FALSE) {
      fossil.tips = is.extinct(tree, tol = 1e-06)
      sa.tips = tree$tip.label[tree$edge[, 2][(tree$edge[, 
        2] %in% 1:length(tree$tip.label)) & (tree$edge.length == 
        0)]]
      unsampled.tips = fossil.tips[!(fossil.tips %in% 
        sa.tips)]
      tree = ape::drop.tip(tree, unsampled.tips)
      node.ages = n.ages(tree)
    }
    trees[[i]] = tree
    trees[[i]]$root.edge = origin - max(node.ages)
    trees[[i]] = SAtree(trees[[i]], complete)
  }
  return(list(f, trees))
}
```

Use modified function sfrt to create func for our project. Output, my_tree (Part 2)
```{r}
modifiedSFBD <- function(n_extant, n_trees, df, lambda, mu, psi, row, mers){
  
  num <- max(c(length(mu), length(lambda), length(psi)))
  
  if(length(mu) == 1){
    m1 <- rep(df[row, mu], times = num)} else{ 
      m1 <- c()
      for(i in mu){m1 <- append(m1, df[row, i])}}
  
  if(length(lambda) == 1){
    l1 <- rep(df[row, lambda], times = num)} else{
      l1 <- c()
      for(i in lambda){l1 <- append(l1, df[row, i])}}
  
  if(length(psi) == 1){
    p1 <- rep(df[row, psi], times = num)} else{
      p1 <- c()
      for(i in psi){p1 <- append(p1, df[row, i])}} #add to p1
  
  modelledfoss <- sfrt(n_extant, n_trees, l1, m1, p1, times = mers, complete = TRUE) #using sfrt
  return(modelledfoss)
}
my_tree <- modifiedSFBD(666, 1, mynewfoss, lambda = "lambda", mu = "mu", psi = c("psi.1.", "psi.2."), 244, c(0, 61))
```
wooohoo it worked!

now for the count.fossils and .binned
```{r}
count.fossils(my_tree[[1]]) # 24
count.fossils.binned(my_tree[[1]], c(0,61)) #15,9
origin_time <- tree.max(my_tree[[2]][[1]], root.edge = TRUE) #158
```
remember tree.max already worked earlier as well...

Make a new column in my_tree (average of hmin and hmax):
```{r}
my_tree[[1]]$h <- ((my_tree[[1]]$hmin + my_tree[[1]]$hmax)/2)
```

## Making a func to print out all three summary stats

### Attempt 1
```{r}

combined_summary <- function(tree, times) {
    
    total_foss <- count.fossils(tree[[1]])
    interval_foss <- count.fossils.binned(tree[[1]], times)
    origin_time <-  tree.max(tree[[2]][[1]])
  
    return(list(total_foss, interval_foss, origin_time))
}
summary <- combined_summary(my_tree, c(0, 61)) 

```
improvements: how to not have to write [[m]] or [[m + 1]]

tried to change names of my_tree list... not a good idea
then tried to see how else to index

### Attempt 2
First way to index was just use the numbers, like [[1]]. Can also use booleans (T for the element chosen, F for not)... 
  problem, not reading the elements in the list when apply count.fossils. It's reading the [[1]], then   rows 1,2,3... instead of going directly to rows 1, 2,3... 
EEP figured out! To access the list inside the fossils list, gotta do the two brackets [[]] and since there's only one list within, just have one logical.
```{r}
## my_tree[c(T,F)] # lists the first element/list in my_tree. BUT =/= my_tree[[1]]

combined_summary2 <- function(tree, times) {
  
    total_foss = count.fossils(tree[[(T)]])
    
    interval_foss =  count.fossils.binned(tree[[(T)]], times)
    
    origin_time = tree.max(tree[c(F, T)] [[T]] [[T]] )
    
    my_list2 <- list(total_foss, interval_foss, origin_time)
    
    names(my_list2) <- c("total_fossils", "interval_fossils", "origin_time")
  
    return(my_list2)
}

summary2 <- combined_summary2(my_tree, c(0, 61))
```
omfg yay! Improvements: still messy, especailly the tree.max... 

another way to name list (but messy looking): my_listNAMES <- (name1 = count_fossils,
                     interval_foss = interval_fossils,
                     origin_time = origin) 

Could also list them out as a vector: c(total_foss, interval_foss, origin_time)
